Software Citation Principles

### 2016-02-24 sc-principles/software-citation-principles.tex
rewording slightly to avoid the multiples of the same word; adding missing words

The Force11 Software Citation Working Group~\cite{f11scwg} was created in April 2015.
It gathered members, and then in June 2015 began studying this, with a number of meetings
and some off-line work by group members to gather materials documenting existing
practices in member disciplines; gather materials from workshops and other reports;
review those materials, identifying overlaps and differences; and draft this resulting document.
This document will be presented and discussed at the Force2016 Conference \cite{force2016}
in April 2016.  We expect that
this discussion may lead to a second, final version of this document, and we also
plan to have a follow-on working group that will work with stakeholders to ensure that
these principles impact the scientific process.

In the next section (\S\ref{sec:use_cases}), we provide some detailed context in which
software citation is important, by means of use cases.  In \S\ref{sec:related_work}, we
summarize and analyze a large amount of previous work and thinking in this area.  In
\S\ref{sec:principles}, we provide set of guiding principles for citation of software within
scholarly literature, other software dataset, or any other research object.  Finally,
in \S\ref{sec:examples} we give examples of how these software citation principles
could be applied, related back to the use cases in \S\ref{sec:use_cases}.

>>>>

The Force11 Software Citation Working Group~\cite{f11scwg} was created in April 2015.
It gathered members, and then in June 2015 began studying this, with a number of meetings
and some off-line work by group members to gather materials documenting existing
practices in member disciplines; gather materials from workshops and other reports;
review those materials, identifying overlaps and differences; and draft this resulting document,
which will be presented and discussed at the Force2016 Conference \cite{force2016}
in April 2016.  We expect that
this discussion may lead to a second, final version, and we also
plan to have a follow-on working group that will interact with stakeholders to ensure that
these principles impact the scientific process.

In the next section (\S\ref{sec:use_cases}), we provide some detailed context in which
software citation is important, by means of use cases.  In \S\ref{sec:related_work}, we
summarize and analyze a large amount of previous work and thinking in this area.  In
\S\ref{sec:principles}, we provide a set of guiding principles for citation of software within
scholarly literature, other software, datasets, or any other research object.  Finally,
in \S\ref{sec:examples} we give examples of how these software citation principles
could be applied, related back to the use cases in \S\ref{sec:use_cases}.
